### 2023-01-18 paper.tex
Feedback for abstract and Section I

	First-generation blockchains (e.g., Bitcoin, Litecoin) essentially provide a distributed ledger consisting of append-only blocks, where the trusted central authority is replaced by a network of nodes that share compute power~\cite{blockchainsurvey}. The second generation of blockchains was proposed in 2014 in the Ethereum white paper \cite{ethpaper}, introducing the concept of smart contracts---user-defined pieces of code that reside on the blockchain and are invoked when their accounts are transacted with. Smart contracts are executed in an environment provided by the respective blockchain that is responsible for executing the instructions in the smart contract and taking care of the consequences. The first and the most important example of such an environment is the Ethereum Virtual Machine (EVM) that is responsible for defining and enforcing the rules that govern the computation of a new valid state after the inclusion of a block. The EVM maintains the Ethereum network as a \textit{distributed state machine}, consisting of a state and an associated set of transactions. The structure of the EVM is described in the Ethereum Yellow Paper ~\cite{wood2019ethereum}. As Ethereum and similar second generation blockchains grow in popularity, the number of deployed smart contracts is growing in number, with the development of newer cryptocurrencies with an emphasis on financial inclusion. Smart contracts provide a way to generate new cryptocurrency tokens, known as \textit{application level tokens} on existing networks without the need to define a new protocol~\cite{commonshood}.

@@

	Code mining approaches involve detecting patterns from a repository of source files and analyzing the purpose those patterns serve. Existing code mining approaches mainly involve extracting business logic, automating the translation of code in one language to another, provisioning searching and indexing source files, detecting similarities (used primarily in detecting code smells), to summarize and visualize algorithms and also to extract and analyze information from source code metadata~\cite{codeminingsurvey}.

	However, the principal difference between optimizing conventional programs and smart contracts lies in the fact that smart contracts have to be optimized primarily in terms of the gas cost~\cite{superoptimization}. The smart contract code, when deployed on the Ethereum network, is compiled into \textit{bytecode}. The bytecode is a string made of concatenated op-codes that are executed in sequence when the smart contract is invoked~\cite{wood2019ethereum}. The execution of each opcode is associated with a certain energy consumption, which is calculated and charged from the user accoording to the EVM \textit{gas model} ~\cite{wood2019ethereum}. This means that optimizing and analyzing smart contracts need to be done not only at the level of the source code, but also at the corresponding bytecode. Optimizing smart contract code directly implies optimizing the gas cost through the bytecode. This introduces an additional constraint and hence requires techniques for constraint-optimized pattern recognition \cite{utilitypattern}.

@@

	Apart from code smell detection and optimization, which was our primary research direction, we believe that this repository can be helpful to researchers in a wide range of other application areas. Code recommendation systems use publicly available code on the Internet to suggest useable pieces of source code to software developers. With the recent progress and development of large language models (LLMs), code generation models such as Codex~\cite{codex} are being used by developers to speed up software design and development, and are proving to be a viable business models for companies. Apart from recommender models focused on source code, general purpose LLMs such as ChatGPT, which is a version of GPT-3 fine-tuned for factoring in human feedback ~\cite{chatgpt} also use large datasets of source code in order to make the token embeddings as generalized and diverse as possible~\cite{thestack}. Such models can also be used for code and algorithm summarization and visualization~\cite{codesummarization}. In security research, commits of source code repositories can be used to analyze patterns in code that eliminate or introduce certain vulnerabilities~\cite{securitydataset}. A dataset of source code can also be used to evaluate and benchmark the performance of static and dynamic analysis tools, which can also be used to detect software vulnerabilities~\cite{staticanalysis}. Analysis of code repositories can also provide useful to generate developer guidelines on writing clean and maintainable code~\cite{maintainablecode}, in the evaluation of software test methods\cite{testmethodevaluation}, in the structural and stylistic comparison of code written in different environments~\cite{codestylecomparison} and in many other studies.

	Ethereum was the first blockchain to introduce smart contracts and the high level language Solidity to program smart contracts in. Solidity has grown to be the most mature and popular programming language for smart contracts~\cite{soliditycheck}. A majority of the contracts available on GitHub is written in for the Ethereum blockchain, in Solidity~\cite{empiricalgithubcontracts}, and hence, solidity was the language of choice in preparing the dataset.  The dataset is compiled by crawling through and scraping publicly accessible repositories on GitHub that have Solidity as the main language. The repositories are identified and all available commits of each file are downloaded using the GitHub API. Due to the varying licenses of GitHub repositories, the dataset is being distributed in the form of a Python script which can be run to scrape GitHub and prepare the dataset in an SQLite database. During experimentation, the script collected 163,961 files from 1021 repositories.

	Section \ref{sec:related} mentions the relevant and existing work, section \ref{sec:requirements} analyses the requirements for preparing the repository, section \ref{sec:implementation} describes how the script was implemented and how it generates and stores the reposirtory, section \ref{sec:limitations} lists out the limitations of the existing approach and \ref{sec:conclusion} concludes the paper and lays the foundation for future work.

>>>>

	First-generation blockchains (e.g., Bitcoin, Litecoin) essentially provide a distributed ledger consisting of append-only blocks, where the trusted central authority is replaced by a network of nodes that share compute power~\cite{blockchainsurvey}. The second generation of blockchains was proposed in 2014 in the Ethereum white paper \cite{ethpaper}, introducing the concept of smart contracts---user-defined pieces of code that reside on the blockchain and are invoked when their accounts are transacted with. Smart contracts are executed in an environment provided by the respective blockchain that is responsible for executing the instructions in the smart contract and taking care of the consequences. The first and the most important example of such an environment is the Ethereum Virtual Machine (EVM) that is responsible for defining and enforcing the rules that govern the computation of a new valid state after the inclusion of a block. The EVM maintains the Ethereum network as a \textit{distributed state machine}, consisting of a state and an associated set of transactions~\cite{wood2019ethereum}. %The structure of the EVM is described in the Ethereum Yellow Paper .

	As Ethereum and similar second generation blockchains grow in popularity, the number of deployed smart contracts is growing in number, with the development of newer cryptocurrencies with an emphasis on financial inclusion. Smart contracts provide a way to generate new cryptocurrency tokens, known as \textit{application level tokens} on existing networks without the need to define a new protocol~\cite{commonshood}.\todo{Do we really need this last sentence here? Actually, I think that everything written from ``in number'' is not absolutely necessary, since it does not address the core topics of our work.}

@@

	Code mining approaches involve detecting patterns from a repository of source files and analyzing the purpose those patterns serve. Existing code mining approaches mainly involve extracting business logic, automating the translation of code in one language to another, provisioning searching and indexing source files, detecting similarities (used primarily in detecting code smells), to summarize and visualize algorithms and also to extract and analyze information from source code metadata~\cite{codeminingsurvey}.\todo{There is a little bit of a logical gap between this paragraph and the next one. Here, you write about general code mining, in the next about optimization. Try to bridge that gap a little bit.}

	However, the principal difference between optimizing conventional programs and smart contracts lies in the fact that smart contracts have to be optimized primarily in terms of the gas cost~\cite{superoptimization}. The smart contract code, when deployed on the Ethereum network, is compiled into \textit{bytecode}. The bytecode is a string made of concatenated op-codes that are executed in sequence when the smart contract is invoked~\cite{wood2019ethereum}. The execution of each opcode is associated with a certain energy consumption, which is calculated and charged from the user accoording to the EVM \textit{gas model} ~\cite{wood2019ethereum}. This means that optimizing and analyzing smart contracts need to be done not only at the level of the source code, but also at the corresponding bytecode. Optimizing smart contract code directly implies optimizing the gas cost through the bytecode. This introduces an additional constraint and hence requires techniques for constraint-optimized pattern recognition \cite{utilitypattern}.\todo{Since the current version of the repository does not provide the bytecode, do we really want to highlight it here. Also, again, there is a logical/storyline gap between this paragraph and the next one, which should be bridged.}

@@

	Apart from code smell detection and optimization for smart contracts, which is our primary research direction, we believe that this repository can be helpful to researchers in a wide range of other application areas. For instance, code recommendation systems use publicly available code on the Internet to suggest usable pieces of source code to software developers. With the recent progress and development of large language models (LLMs), code generation models such as Codex~\cite{codex} are being used by developers to speed up software design and development, and are proving to be a viable business models for companies. Apart from recommender models focused on source code, general purpose LLMs such as ChatGPT, which is a version of GPT-3 fine-tuned for factoring in human feedback~\cite{chatgpt} also use large datasets of source code in order to make the token embeddings as generalized and diverse as possible~\cite{thestack}. Such models can also be used for code and algorithm summarization and visualization~\cite{codesummarization}. In security research, commits of source code repositories can be used to analyze patterns in smart contract code that eliminate or introduce certain vulnerabilities~\cite{securitydataset}. A dataset of source code can also be used to evaluate and benchmark the performance of static and dynamic analysis tools, which can also be used to detect software vulnerabilities~\cite{staticanalysis}. Analysis of code repositories can also provide useful to generate developer guidelines on writing clean and maintainable code~\cite{maintainablecode}, in the evaluation of software test methods\cite{testmethodevaluation}, in the structural and stylistic comparison of code written in different environments~\cite{codestylecomparison} and in many other studies. \todo{Very fine abstract, showing the need for the work at hand. However, again a logical gap to the next paragraph (i.e., the one about Ethereum).}

	The multitude of potential research areas which are based on source code shows the need for the Smart Contract Repository presented in the work at hand.\todo{Please extend this paragraph by writing down what we are actually delivering in this paper.}

	Ethereum was the first blockchain to introduce smart contracts and the high level language Solidity to program smart contracts in. Solidity has grown to be the most mature and popular programming language for smart contracts~\cite{soliditycheck}. A majority of the contracts available on GitHub is written for the Ethereum blockchain, in Solidity~\cite{empiricalgithubcontracts}\todo{I do not see that the referenced paper shows this.}, and hence, Solidity was the language of choice in preparing the dataset\todo{Since it is not described yet what the paper will deliver, the reader actually does NOT know what this ``dataset'' is referring to. If I just read this particular paragraph, I would think that only a dataset is delivered (what we do not do!).}.  The dataset is compiled by crawling through and scraping publicly accessible repositories on GitHub that have Solidity as the main language. The repositories are identified and all available commits of each file are downloaded using the GitHub API. Due to the varying licenses of GitHub repositories, the dataset is being distributed in the form of a Python script which can be run to scrape GitHub and prepare the dataset in an SQLite database. During experimentation, the script collected 163,961 files from 1021 repositories.\todo{I do not like this paragraph too much, since it mixes things up quite a lot. First, it tries to justify why Solidity is used, which is fine (however, better grounding in the literature is necessary). However, afterwards, there is a mixture of repository functionalities and outcomes in terms of the the collected files. Please separate these parts better; this shows also again that it is necessary to first clearly describe what this paper is going to deliver. On another note: I also do not think that the problem with the licenses is highlighted here in enough detail. It's actually mentioned only very very briefly. I do not know if this is taken up later on again, but from I read here, I would not understand (as a normal reader) why there is actually a need for the script at all.}

	The remainder of this paper is structured as follows: In Section~\ref{sec:prelims}, we define  prerequisites for our approach. 	Afterwards, Section~\ref{sec:related} discusses the relevant and existing work, Section~\ref{sec:requirements} analyses the requirements for preparing the repository, Section~\ref{sec:implementation} describes how the script\todo{Again, I am not sure if it is too good to write here about the ``script'' alone.} was implemented and how it generates and stores the repository. Finally, Section~\ref{sec:limitations} discusses some limitations of the existing approach and Section~\ref{sec:conclusion} concludes the paper and lays the foundation for future work.
